---
title: "Analysis: [FILL IN — short working title]"
format: html
execute:
  echo: true
  warning: false
  message: false
---

<!--
This file is the reproducible analytical record: every cleaning step,
model, and figure lives here. index.qmd stays text-only and just
references the outputs this file produces. See the full guide at
https://olivierraven.github.io/Open_Research_Workflow/ for why.
-->

## Setup

```{r}
#| label: setup
library(tidyverse)

# FILL IN: add any other packages you need, e.g. library(brms)
```

## Load raw data

`data/raw/example_data.csv` is placeholder data shipped with this template so
the project renders out of the box. **Replace it with your own file(s) in
`data/raw/` and update the path below** — never edit anything inside
`data/raw/` by hand once real data lands there.

```{r}
#| label: load-data
data <- read_csv("data/raw/example_data.csv")
glimpse(data)
```

## Data cleaning

```{r}
#| label: data-cleaning

# FILL IN: replace with your own cleaning logic. This example drops rows
# with a missing measurement and derives a grouping variable.
data_clean <- data |>
  filter(!is.na(measurement)) |>
  mutate(treatment = factor(treatment, levels = c("control", "treatment")))

write_csv(data_clean, "data/derived/example_data_clean.csv")
```

## Summary table

```{r}
#| label: tbl-summary
#| tbl-cap: "FILL IN — table caption"

summary_table <- data_clean |>
  summarise(
    n = n(),
    mean = mean(measurement),
    sd = sd(measurement),
    .by = treatment
  )

write_csv(summary_table, "outputs/tables/summary_table.csv")
summary_table
```

## Statistical model

```{r}
#| label: model-example
#| cache: true

# FILL IN: replace with your actual model. This is a placeholder t-test
# standing in for whatever analysis your question needs.
model_result <- t.test(measurement ~ treatment, data = data_clean)
saveRDS(model_result, "outputs/model_result.rds")
model_result
```

## Figure

```{r}
#| label: fig-example
#| fig-cap: "FILL IN — figure caption"

fig_example <- ggplot(data_clean, aes(x = treatment, y = measurement, fill = treatment)) +
  geom_boxplot() +
  geom_jitter(width = 0.15, alpha = 0.5) +
  scale_fill_manual(values = c("#2E7D6B", "#A8D5C8")) +
  labs(x = "Treatment", y = "Measurement") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("outputs/figures/fig-example.png", fig_example, width = 7, height = 5, dpi = 300)
fig_example
```

## Session info

Keep this at the end of every analysis file — a second line of defence
alongside `renv.lock` for anyone trying to reproduce your work.

```{r}
#| label: session-info
sessionInfo()
```
